A new model to predict survival in patients with end-stage liver disease

### 2022-07-19 analysis/article.Rmd
feat: extend figure captions

```{r flowchart, results = "asis", echo = FALSE, fig.width = 4.5, fig.height = 2, fig.cap = "Flowchart Inclusion/Exclusion."}
library("consort")
library("grid")

@@

```{r roc, fig.width = 7, fig.height = 7, echo = FALSE, message = FALSE}
col <- viridisLite::viridis(5)
m <- list(
    AMELD = timeROC_RCV,
    MELD = timeROC_MELD,
    "MELD-Na" = timeROC_MELDNa,
    "MELD-Plus7" = timeROC_MELDPlus7
)
invisible(roc <- plot_surv_roc(m, timepoint = 90, col = col[-2]))
roc <- roc[order(-roc)]
```

>>>>

```{r flowchart, results = "asis", echo = FALSE, fig.width = 4.5, fig.height = 2, fig.cap = "Flowchart. Inclusion and exclusion of records."}
library("consort")
library("grid")

@@

The final model was compared against the MELD, MELD-Na and MELD-Plus7 score
using the area under the time-dependent receiver operating characteristic curve
(AUROC) based on the nonparametric inverse probability of censoring weighting
estimator (IPCW) [@blanche2013, @R-timeROC].
Testing was applied as described in @blanche2013.

```{r roc, fig.width = 7, fig.height = 7, echo = FALSE, message = FALSE, fig.cap = "Receiver operating characteristic (ROC) curve. Area under the time-dependent receiver operating characteristic curve (AUROC) based on the nonparametric inverse probability of censoring weighting estimate (IPCW) for AMELD, MELD, MELD-Na and MELD-Plus7 as described in [@blanche2013]."}
col <- viridisLite::viridis(5)
m <- list(
    AMELD = timeROC_RCV,
    MELD = timeROC_MELD,
    "MELD-Na" = timeROC_MELDNa,
    "MELD-Plus7" = timeROC_MELDPlus7
)
invisible(roc <- plot_surv_roc(m, timepoint = 90, col = col[-2]))
roc <- roc[order(-roc)]
```
